SoK: Application Attack Defenses (in Question)

### 2014-09-23 docs/questioning.tex
added a note for the suffixes
added one bibtex entry

As in medical diagnostic tests, application attack defense mechanisms
must demonstrate the presence of an attack. This, however, does not
make an application attack defense mechanism immediately useful. In
order for a detection mechanism to be useful it must be accurate, easy to
use, and economical. The accuracy of a detection mechanism is gauged
with the following metrics:
\begin{itemize}
\item {\bf Sensitivity}, the probability that an attack will be
  caught.
\item {\bf Specificity}, the probability that a normal interaction
  will test negative.
\item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
  reported attack is a real attack.
\item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
  nothing is reported no attack has taken place.
\end{itemize}

@@

	&&& \bf{TP,TN,FP,FN}

@@

>>>>

As in medical diagnostic tests, application attack defense mechanisms
must demonstrate the presence of an attack. This, however, does not
make an application attack defense mechanism immediately useful. In
order for a detection mechanism to be useful it must be accurate, easy to
use, and economical. The accuracy of a detection mechanism is gauged
with the following metrics~\cite{GFDLS06,A00}:
\begin{itemize}
\item {\bf Sensitivity}, the probability that an attack will be
  caught.
\item {\bf Specificity}, the probability that a normal interaction
  will test negative.
\item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
  reported attack is a real attack.
\item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
  nothing is reported no attack has taken place.
\end{itemize}

@@

	&&& \bf{TP,TN,FP,FN}\tnote{2}

@@

		\item[2] For every quadruple there is a corresponding suffix that indicates whether the testbed was
	based on real-world applications known to be vulnerable ({\it r}), synthetic benchmarks ({\it s}) or both ({\it a}).
	If no testing has taken place we add a question mark ({\bf ?}).
